Optimization of String Rewriting Operations for 3D Fractal Generation with Genetic Algorithms

### 2018-03-25 Optimization-of-String-Rewriting-Operations-for-3D-Fractal-Generation-with-Genetic-Algorithms/paper.tex
Introduction part was finished.

In Hodkinson's research genetic algorithms (GAs) were employed in order 2D shape of Greek letter $\pi$ to be reconstructed with substitution rules of 30 shades of blue pixels (Fig. \ref{fig:pic01}). The key problem in his research was wich 30 rules to be selected in order the final goal to be achieved. GAs were a promising approach for such kind of combinatorial optimization. A single rule had LHS pixel with particular color and nine pixels on the RHS as 3x3 substitution matrix. Image starts with a single pixel and it grows on size by 3 on each generation.

\section{Optimization} \label{Optimization}

\section{Experiments} \label{Experiments}

>>>>

In Hodkinson's research genetic algorithms (GAs) were employed in order 2D shape of Greek letter $\pi$ to be reconstructed with substitution rules of 30 shades of blue pixels (Fig. \ref{fig:pic01}). The key problem in his research was wich 30 rules to be selected in order the final goal to be achieved. GAs were a promising approach for such kind of combinatorial optimization. A single rule had LHS pixel with particular color and nine pixels on the RHS as 3x3 substitution matrix. Image starts with a single pixel and it grows on size by 3 on each iteration.

This study extends the same idea from 2D space into 3D space. Voxels are used instead of pixels. Square matrix of 3x3 is replaced with cube 3x3x3. The paper is organized as follows: Section \ref{Introduction} introduces the problem; Section \ref{Model and Optimization} presents a model and optimization approach; Section \ref{Experiments and Results} gives some experiment details and some results are shown; Section \ref{Conclusions} concludes and some further ideas for research are pointed.

\section{Model and Optimization} \label{Model and Optimization}

\section{Experiments and Results} \label{Experiments and Results}
